\Large \bf Compilers Project: PTX Super-optimization

### 2018-04-30 paper/main.tex
now with disjoint outputs

The search for \texttt{add.u32 d, a, 0;} is complicated by potential encoding
troubles that will be mentioned later. Instead of producing the simple
identity, the program complicates matters:
\begin{lstlisting}
sub.u32 t0, f, f;
add.u32 d, a, t0;
\end{lstlisting}
This may be due to semantics in bit-vector theory that require
further investigation.

@@

@@

@@

>>>>

The search for \texttt{add.u32 d, a, 0;}
terminates in the idempotent generation phase and is fairly quickly.

@@

\subsection{Disjoint Outputs: an Optimization}

@@

%This is slow!
One instruction processing and the processing of identities is not only fast
but rather pleasant to see working.

From observation, it appears that multiplication is the slowest and most
difficult to process instruction. This may be due to the semantics of the
encoding. For a \texttt{mul.lo.u32 d, x, y;} for instance, the following SAT query
is produced: \texttt{Extract(0 to 32, Zero-Extend(x, 64), Zero-Extend(y, 64)) == d}.
This query may be much slower to process.

@@

Additionally, the current implementation does not handle constants. In theory,
this is not a huge hinderance: the optimizer may as well treat them as extra
inputs, especially since pre-conditions and post-conditions are not handled.
An extension would not only include constants, but use them to infer stronger
conditions on the program.
